WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-22 paper/ms.tex
update author list

\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu WAITING

@@

\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu WAITING
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA }

@@

\author{S. Seager} % seager@mit.edu WAITING

@@

\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov WAITING

@@

\author[0000-0002-3321-4924]{Z. Berta-Thompson} % Zachory.BertaThompson@Colorado.EDU WAITING

@@

\author[0000-0003-1963-9616]{D. A. Caldwell} % douglas.Caldwell@nasa.gov % WAITING

@@

\author[0000-0001-8020-7121]{K. Col\'on} % knicole.colon@nasa.gov WAITING

@@

\author{M. Fausnaugh} % faus@mit.edu WAITING

@@

\author{N. Guerrero} % nmg@mit.edu WAITING

@@

\author[0000-0001-8812-0565]{J. Rodriguez} % rodriguez.jr.joey@gmail.com WAITING
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA }

@@

\author[0000-0002-6778-7552]{J. D. Twicken} % Joseph.Twicken@nasa.gov WAITING

@@

\author{B. Wohler} % bill.wohler@nasa.gov WAITING

>>>>

\author[0000-0001-6763-6562]{R. Vanderspek} % roland@space.mit.edu CONFIRMED

@@

\author[0000-0001-9911-7388]{D. W.~Latham} % dlatham@cfa.harvard.edu CONFIRMED
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

@@

\author{S. Seager} % seager@mit.edu CONFIRMED

@@

\author[0000-0002-4715-9460]{J. M.~Jenkins} % jon.jenkins@nasa.gov CONFIRMED

@@

\author[0000-0002-3321-4924]{Z. Berta-Thompson} % zachory.bertathompson@colorado.EDU CONFIRMED

@@

% \author[0000-0003-1963-9616]{D. A. Caldwell} % douglas.caldwell@nasa.gov % WAITING
% \affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
% \affiliation{ SETI Institute, Mountain View, CA 94043, USA}

@@

\author[0000-0001-8020-7121]{K. Col\'on} % knicole.colon@nasa.gov CONFIRMED

@@

% \author{M. Fausnaugh} % faus@mit.edu WAITING
% \affiliation{ Department of Physics and Kavli Institute for Astrophysics
% and Space Research, Massachusetts Institute of Technology, Cambridge, MA
% 02139, USA }

@@

% \author{N. Guerrero} % nmg@mit.edu WAITING
% \affiliation{ Department of Physics and Kavli Institute for Astrophysics
% and Space Research, Massachusetts Institute of Technology, Cambridge, MA
% 02139, USA }

@@

\author[0000-0001-8812-0565]{J. E. Rodriguez} % rodriguez.jr.joey@gmail.com CONFIRMED
\affiliation{Center for Astrophysics \textbar \ Harvard \&
Smithsonian, 60 Garden St, Cambridge, MA 02138, USA}

@@

\author[0000-0002-6778-7552]{J. D. Twicken} % joseph.twicken@nasa.gov CONFIRMED

@@

% \author{B. Wohler} % bill.wohler@nasa.gov WAITING
% \affiliation{ NASA Ames Research Center, Moffett Field, CA 94035, USA }
% \affiliation{ SETI Institute, Mountain View, CA 94043, USA}
